---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.align = "center"
)
set.seed(130)
```

# jokeR

## Installation

```{r, eval = FALSE}
# Install development version from GitHub
# install.packages("devtools")
devtools::install_github("AQLT/jokeR")
```

## Usage

To print a random joke you can use the function `random_joke()`:
```{r, eval = FALSE}
library(jokeR)
random_joke()
```

You can also specify from which database you want a random joke and on which categories (use `joke_categories()` to check the available ones). For example to only have jokes religious and animal jokes:
```{r, eval = FALSE}
random_joke(categories = c("Animal", "Animals", "Religious"))
```

To print a message each time you open your session the most simple is to edit your `Rprofile.site` file. If R is installed in `C:\Program Files\R\R-n.n.n` this file will be located in the `C:\Program Files\R\R-n.n.n\etc` directory. You can also use the function:

```{r, eval = FALSE}
edit_rprofile.site()
```

Then, if you use RStudio, you can add the following command to print a message each time you open RStudio (thanks [davidgohel](https://github.com/davidgohel) for the tip!):

```{r, eval = FALSE}
setHook("rstudio.sessionInit", function(newSession) {
  if (newSession){
    print(jokeR::random_joke())
  }
}, action = "append")
```
Otherwise you can also change the `.First()` function:
```{r, eval = FALSE}
.First <- function() {
  print(jokeR::random_joke())
}
```

## Databases

For the moment the database are from https://github.com/taivop/joke-dataset (jokes from stupidstuff and wocka).


## Futur developments

Have more and smaller databases on various topics: jokes, citations, poems, etc.  
Add category argument to jokes.


